\textbf{Response Letter}

### 2018-12-21 doc/aij18/major-revision/letter.tex
Updates in response letter

\begin{enumerate}
\item \textbf{Introduction}. We performed a profound revision of the Introduction in order to make it more self-explanatory. First, we carefully revised all of the comments pointed by reviewer \#2. Additionally, as indicated by reviewer \#1, we provide an outline of the overall picture of our \FAMA approach. Our modification is intended to adequately position our contribution within the concerned research field, and to provide a global picture of \FAMA that explains our pursued objective. In this section, we have introduced a new paragraph that descriptively presents the functioning of \FAMA. Additionally, at the end of the section we highlight the main distinctive characteristics of \FAMA which describe the overall concept of our learning approach.

\item \textbf{Problem definition and complexity}. As indicated by reviewer \#2, and also supported by reviewers \#1 and \#3, the problem definition is not clearly introduced. We believe this is the reason that our claims about the complexity of the learning task were not fully comprehensible. We acknowledge this lack of problem definition, and we introduce a subsection 3.1 to clearly define upfront the basic and essence of the learning task we are aimed to solve.

@@

@@

>>>>

\begin{enumerate}
\item \textbf{Introduction}. We thoroughly revised the Introduction to make it more self-explanatory. First, we carefully revised all of the comments pointed by reviewer \#2. Additionally, as indicated by reviewer \#1, we provide an outline of the overall picture of our \FAMA approach. Our modification is intended to adequately position our contribution within the concerned research field, and to provide a global picture of \FAMA that explains our pursued objective. For this purpose, we have introduced a new paragraph that descriptively presents the functioning of \FAMA. Additionally, at the end of the section we highlight the main distinctive characteristics of \FAMA which describe the overall concept of our learning approach.

\item \textbf{Problem definition and complexity}. As indicated by reviewer \#2, and also supported by reviewers \#1 and \#3, the problem definition was not clearly introduced. We believe this is the reason that our claim about using planning for solving the learning task was not fully comprehensible. We have reshaped the old section 3 (Motivation), which now is entitled "Learning task: on the use of planning for solving the task". First, we introduce the definition of the learning task (which was in section 4 in the previous version of the paper), and then we analyze the intricacies of the learning task to the different variants of observed plan traces. We organised the explanation around two well differentiated cases: when the observation identifies the length of the plan being executed and when it does not. Now, the discussion revolves around the particularities of solving the learning task in these two cases and we make some side comments on the complexity of the task. Hopefully, the significant remodeling of this section will clarify the need of using planning techniques for solving the learning task.

@@

\textcolor{blue}{Following the reviewer's advice, we have substantially changed section 3. We refer the reviewer to our main modification \#2. We removed the complexity table of page 8 and we now focus the discussion around the two main cases that determine the difficulty of the learning task, giving an indication of the task complexity according to the characteristics that define these two cases. We also changed the reference and added instead the original work that proves that boolean SAT problems are NP-complete.}

@@

\textcolor{blue}{The reviewer is totally right in that planning is needed when the length of the solution plan is unknown. Precisely, this is the point that motivates our approach but that we did not successfully convey in the previous version of the paper. When the observed plan trace comprises a partially observed action sequence and a partially observed state trajectory, we ignore the length of the solution plan and so we need to resort to planning. The new section 3 explains this in detail (main modification \#2). When the length of the plan is known, SAT-solvers can be used; when it is not known, planning is required. The fact that we used a SAT-based planner to solve the learning task is principally motivated by the ability of Madagascar to detect dead-end nodes.}
